Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-01-22 doc/network.tex
caption

\begin{figure}
\includegraphics[width=\textwidth]{../fig/local_effect.pdf}
\caption{Fill this out.}
\label{fig:local}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/example.pdf}
\caption{Fill this out.}
\label{fig:example}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/compare_methods.pdf}
\caption{Fill this out.}
\label{fig:test}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/cmp_reproductive.pdf}
\caption{Fill this out.}
\label{fig:cmp}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{../fig/local_effect.pdf}
\caption{
\textbf{Comparison of spatial effects on the realized generation intervals.}
(Left) The intrinsic generation-interval distribution corresponds to the distribution of all infectious contacts that were made, regardless of the outcome (i.e., whether it resulted in infection or not); 5000 stochastic simulations were performed on a tree network with 5 nodes (1 infector and 4 susceptibles).
(Middle) The egocentric generation-interval distribution corresponds to the distribution of all infectious contacts made by a single primary infector that gave rise to infection; 5000 stochastic simulations were performed on a tree network with 5 nodes (1 infector and 4 susceptibles).
(Right) The realized generation-interval distribution corresponds to the distribution of all infection times throughout an epidemic; 5000 stochastic simulations were performed on a homogeneous network with 5 nodes (1 infector and 4 susceptibles).
\swp{Parameters? High per-pair contact? Need to describe and make the figure prettier}
}
\label{fig:local}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/example.pdf}
\caption{\swp{Need to re-do this figure; initial overestimation of little $r$ is weird}}
\label{fig:example}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/compare_methods.pdf}
\caption{\swp{Need to re-do this figure; initial overestimation of little $r$ is weird}.}
\label{fig:test}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{../fig/cmp_reproductive.pdf}
\caption{\textbf{Comparison of estimates of reproductive number based on various methods}
Using the observed generation-interval distributions without correcting for right-censoring severely underestimates the reproductive number.
Similarly, using intrinsic and egocentric generation-interval distributions without accounting for local spatial effects overestimates the reproductive number.
Both population-level and individual-level methods provide estimates of reproductive number that are consistent with the empirical estimates, which we define as the average number of secondary cases generated by the first 100 infected individuals.
100 stochastic simulations were performed on an empirical network [CITE] using Ebola-like parameters (latent period = 11.4 days and infectious period = 5 days).
}
\label{fig:cmp}
\end{figure}
